### 2023-01-23 README.rmd
23 Jan Update

@@

# FMX PROJECT

@@

```{r}

@@

sectors <- T40 %>% pull(Sector) %>% unique()
sector_return <- list()
for(i in 1:length(sectors)){
    # Loop through sectors and calculate returns and cumulative returns
    sector_return[[i]] <- portfolio_return_function(T40, sector = sectors[i]) %>% group_by(Portfolio) %>% 
      mutate(cumreturn_Rand = (cumprod(1 + Returns))) %>% # Start at 1
      mutate(cumreturn_Rand = cumreturn_Rand/dplyr:::first(cumreturn_Rand)) %>% 
      mutate(Sector = sectors[i])
}
# Rename tibbles
names(sector_return) <- sectors
sector_return
# Combine Dataframes
sectors_cum_return <- rbind(sector_return[[1]], sector_return[[2]], sector_return[[3]]) %>% arrange(date)

sectors_cum_return_plot <- sectors_cum_return %>% 
    ggplot() +
    geom_line(aes(date, cumreturn_Rand, colour = Portfolio), alpha = 0.8) + facet_wrap(~Sector) + fmxdat::fmx_cols() + 
    labs(title = "Cumulative Returns per Sector for ALSI and SWIX", y = "Cumulative Returns", x = "") + 
    fmxdat::theme_fmx(title.size = ggpts(25))
sectors_cum_return_plot
```

Subset the data into times of loadshedding and times without.

```{r}
sectors_cum_return <- sectors_cum_return %>% filter(Portfolio == 'J400') # SWIX

@@

Plotting the Log returns of all sectors across the entire period.

```{r}
log_returns_plot <- sectors_cum_return %>% mutate(Sector = factor(Sector, levels = c("Financials",  "Industrials", "Resources"))) %>% 
  ggplot() + geom_line(aes(x = date, y = Returns, colour = Sector, alpha = 1)) + 
#ggtitle("Daily Log Returns") + 
facet_wrap(~Sector, scales = "free_y", nrow = 3) + 
guides(alpha = "none") + 
fmxdat::theme_fmx() +
labs(x = "", y = "", subtitle = " ") +
theme(legend.position = "none") +
scale_color_hue(l = 20) + 
scale_x_date(labels = scales::date_format("%Y"), date_breaks = "1 years") +

theme(axis.text = element_text(size = 7))

@@

## Whole Period

```{r}
# Using the rugarch package, let's specify our own univariate
# functions to be used in the dcc process:

@@

@@

## Plots

@@

```{r}
stargazer(fit.dcc@mfit$matcoef,
          type = "text",
          title = "DCC GARCH Model Fit \\label{dccfitfull}",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE)

#fit.dcc@mfit$matcoef %>% kable() %>% kable_styling()

# add_stars <- function(p) {
#     if (p < 0.001) {
#         return("***")
#     } else if (p < 0.01) {
#         return("**")
#     } else if (p < 0.05) {
#         return("*")
#     } else {
#         return("")
#     }
# }

# fit.dcc@mfit$matcoef[,-3]

# kable(fit.dcc@mfit$matcoef[,-3], caption = "DCC GARCH Model", 
#       col.names = c("Coefficient", "Std. Error", "p-value"), 
#       align = c("l", "c", "c"), 
#       digits = c(2, 2, 3),
#       p.format = add_stars) %>% kable_styling()

```{r, results = 'asis'}
stargazer(fit.dcc_ls@mfit$matcoef,
          type = "text",
          title = "Loadshedding DCC GARCH Model Fit \\label{dccfitls}",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE)
```

```{r, results = 'asis'}
stargazer(fit.dcc_nls@mfit$matcoef,
          type = "text",
          title = "No Loadshedding DCC GARCH Model Fit \\label{dccfitnls}",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE)
```

>>>>

# Purpose

This README is here to describe my analysis with the accompanying code.

This analysis will look at the dynamic conditional correlations of the sector returns of the SWIX. The time period will start at January 1 2014 and end at the most recent date October 29 2021. The data will then be subset for the month periods that South Africa experienced loadshedding. The aim of this paper is to see if there is a difference in sector dynamics between the Financials, Industrials and Resources for the SWIX. The DCC-GARCH model will be used to model the dynamic correlation structure of these returns during these periods of loadshedding and allow us to study the impact of loadshedding on the market.

First we will load necessary packages and source our code files.

@@

Below is the code used to create this file and the Texevier document.

@@

Unfortunately I could not scrape the SWIX portfolio weights for the updated period and have had to use the data given. This leaves us with a slightly smaller sample and also does not include the months of significant loadshedding in 2022.

```{r}
T40 <- read_rds("data/T40.rds")

@@

sectors <- T40 %>% pull(Sector) %>% unique()
sector_return <- list()
for(i in 1:length(sectors)){
    # Loop through sectors and calculate returns and cumulative returns
    sector_return[[i]] <- portfolio_return_function(T40, sector = sectors[i]) %>% group_by(Portfolio) %>% 
      mutate(cumreturn_Rand = (cumprod(1 + Returns))) %>% # Start at 1
      mutate(cumreturn_Rand = cumreturn_Rand/dplyr:::first(cumreturn_Rand)) %>% 
      mutate(Sector = sectors[i])
}
# Rename tibbles
names(sector_return) <- sectors
sector_return
# Combine Dataframes
sectors_cum_return <- rbind(sector_return[[1]], sector_return[[2]], sector_return[[3]]) %>% arrange(date)
```

Below we look at the different return structure of the ALSI and SWIX for their respective sectors. We observe that the Industrials have seen the largest cumulative growth of all sectors. Resources have seen minimal cumulative growth, with majority of the growth being after 2017.

```{r}
sectors_cum_return_plot <- sectors_cum_return %>% 
    ggplot() +
    geom_line(aes(date, cumreturn_Rand, colour = Portfolio), alpha = 0.8) + facet_wrap(~Sector) + fmxdat::fmx_cols() + 
    labs(title = "Cumulative Returns per Sector for ALSI and SWIX", y = "Cumulative Returns", x = "") + 
    fmxdat::theme_fmx(title.size = ggpts(25))
sectors_cum_return_plot
```

## Weights plot

To decide between the ALSI and SWIX I visualise the weight compositions of the indices.

* ALSI (J200)

```{r}
weights_plot(T40, "ALSI")
```

* SWIX (J400)

```{r}
weights_plot(T40, "SWIX")
```

From the plots it can be seen that since 2020 the ALSI lowered their weighting of Financial stocks and increased their weighting of resource stocks in comparison to the SWIX. The SWIX also has less volatility in weight contribution. Because of this the SWIX is chosen as the representative portfolio.

The portfolio returns are then stratified into periods of loadshedding and periods without loadshedding.

```{r message=FALSE, warning=FALSE}
sectors_cum_return <- sectors_cum_return %>% filter(Portfolio == 'J400') # SWIX

@@

The Log returns of all sectors across the entire period are the plotted.

```{r}
log_returns_plot <- sectors_cum_return %>% mutate(Sector = factor(Sector, levels = c("Financials",  "Industrials", "Resources"))) %>% 
  ggplot() + geom_line(aes(x = date, y = Returns, colour = Sector, alpha = 1)) + 
facet_wrap(~Sector, scales = "free_y", nrow = 3) + 
guides(alpha = "none") + 
fmxdat::theme_fmx() +
labs(x = "", y = "", subtitle = " ") +
theme(legend.position = "none") +
scale_color_hue(l = 20) + 
scale_x_date(labels = scales::date_format("%Y"), date_breaks = "1 years") + 
theme(axis.text = element_text(size = 7))

@@

The DCC model is then fit over the whole period, the period of loadshedding and the period without loadshedding. The gjrGARCH model is used for this analysis. The residuals of the GARCH model are then used in the DCC model.

```{r message=FALSE, warning=FALSE}
# Using the rugarch package, let's specify our own univariate
# functions to be used in the dcc process:

@@

The results have to be pulled out of the data using the following code. This will also rename our dynamic conditional correlations.

@@

First we asses the fit of the DCC model on the data.

```{r, results = 'asis'}
library(data.table)
star_fit.dcc <- fit.dcc@mfit$matcoef[rownames(fit.dcc@mfit$matcoef) %like% 'omega|alpha1|beta1|dcca1|dccb1',, drop = FALSE] #%>% data.frame()

# \\label{dccfitfull}

stargazer(star_fit.dcc,
          type = "latex",
          title = "DCC GARCH Model Fit",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE)

```{r, results = 'asis' }
star_fit.dcc_ls <- fit.dcc_ls@mfit$matcoef[rownames(fit.dcc_ls@mfit$matcoef) %like% 'omega|alpha1|beta1|dcca1|dccb1',, drop = FALSE]

# \\label{dccfitls}

stargazer(star_fit.dcc_ls,
          type = "latex",
          title = "Loadshedding DCC GARCH Model Fit",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE) 
```

```{r, results = 'asis'}
star_fit.dcc_nls <- fit.dcc_nls@mfit$matcoef[rownames(fit.dcc_nls@mfit$matcoef) %like% 'omega|alpha1|beta1|dcca1|dccb1',, drop = FALSE]

# \\label{dccfitnls}

stargazer(star_fit.dcc_nls,
          type = "latex",
          title = "No Loadshedding DCC GARCH Model Fit",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE)
```

## DCC Plots

The plots of the dynamic conditional correlations will be plotted for all sectors and their respective relationships. These plots will be repeated for the full period, with an indication of when the loadshedding periods were, as well as for just the loadshedding periods.

@@
